\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{amssymb} % For checkboxes
% \usepackage{array} 
\usepackage{xcolor}
% \usepackage{setspace}
\usepackage{framed}

\setlength{\parindent}{0pt} % Disable paragraph indentation

\begin{document}

\begin{center}
{\fontsize{11pt}{13pt} \selectfont \textbf{Residency Reclassification Questionnaire}} \\
{\fontsize{6pt}{8pt} \selectfont \textbf{This questionnaire is used to determine if a University of Houston student qualifies for resident tuition. The determination of residency classification for tuition purposes is governed by the Texas Education Code, Section 54.052 through 54.064 and rules and regulations promulgated by the Texas Higher Education Coordinating Board. Failure to provide complete and accurate information, supporting documents, and appropriate signatures will delay processing and may result in denial of your application for residency.}}
\end{center}

\textbf{Part A: Student Basic Information} \\[5pt]
You may apply for a future term or the current term before the ORD (Official Reporting Date).
\\
\begin{center}
    \begin{tabular}{c@{\hspace{2cm}}c@{\hspace{2cm}}c}
        \rule{4cm}{0.4pt} & \rule{5cm}{0.4pt} & \rule{3cm}{0.4pt} \\ 
        Name & Date of Birth & Age
        \\ \\ %new line 
        \rule{4cm}{0.4pt} & \rule{5cm}{0.4pt} \\
        Term & Student ID Number
    \end{tabular}
\end{center}

\textbf{Part B: Previous Enrollment} \\[5pt]
1. During the 12 months prior to the term for which you are applying, did you attend a public college or university in Texas in a fall or spring term? (Yes/No) \underline{\hspace{5cm}}
\\ \\
2. If yes, what Texas public institution did you last attend? (Give full name, not just initials) \underline{\hspace{9cm}}
\\ \\
3. In which terms were you last enrolled? (Indicate all that apply)
\\ \\
\begin{left}
    \begin{tabular}{c@{\hspace{2cm}}c@{\hspace{2cm}}c}
    \rule{4cm}{0.4pt} & \rule{5cm}{0.4pt} \\
    Fall, Year & Spring, Year
    \end{tabular}
\end{left}
\\ \\
4. During your last semester at a Texas public institution, did you pay resident (in-state) or nonresident (out-of-state) tuition? Check one.
\begin{list}{}{\leftmargin=0pt \itemindent=0pt \setlength{\itemsep}{0pt}}
    \item $\square$ resident (in-state)
    \item $\square$ nonresident (out-of-state)
    \item $\square$ unknown
\end{list}

5. If you paid in-state tuition at your last institution, was it because you were a Texas resident or because you were a nonresident who received a waiver? Check one.
\begin{list}{}{\leftmargin=0pt \itemindent=0pt \setlength{\itemsep}{0pt}}
    \item $\square$ resident
    \item $\square$ nonresident with a waiver
    \item $\square$ unknown
\end{list}

\textbf{Part E: Basis of Claim to Residency} \\[5pt]
1. Do you file your own federal income tax as an independent taxpayer? {\color{red} If yes, submit your 1040 Federal Income Tax transcript.} A Tax Transcript is a summary of the Tax Return.

An independent taxpayer should not be claimed as a dependent for tax purposes by another person. If you file a joint return with your spouse, answer "yes". (Yes/No).
\vspace{0.6cm}
\underline{\hspace{3cm}}
\\
2. Are you claimed as a dependent or are you eligible to be claimed as a dependent by a parent or court-appointed guardian*? {\color{red} If yes, submit Parent's 1040 Federal Income Tax transcript.} A Tax Transcript is a summary of the Tax Return.

To be eligible to be claimed as a dependent, your parent or legal guardian must provide at least one half of your support. A step-parent does not qualify as a parent if he/she has not adopted the student. (Yes/No).
\vspace{0.6cm}
\underline{\hspace{3cm}}
\\
\textbf{Part F. Questions for students who answered "Yes" to Question 1 or "Self" to Question 3 of Part E} \\[5pt]
1. Are you a U.S. Citizen? (Yes/No).
\vspace{0.6cm}
\underline{\hspace{3cm}}
\\
5. Do you currently live in Texas? If you are out of state due to a temporary assignment by your employer or other temporary purpose, please check "no" and explain in Part H. {\color{red} You may be required to submit additional documentation supporting a temporary employment absence.} (Yes/No).
\vspace{0.6cm}
\underline{\hspace{3cm}}
\\
6a. If you currently live in Texas, how long have you been living here? {\color{red} You may be required to provide a copy of a lease agreement or mortgage agreement.}
\begin{center}
    \begin{tabular}{c@{\hspace{2cm}}c@{\hspace{2cm}}c}
        \rule{4cm}{0.4pt} & \rule{4cm}{0.4pt} \\
        Years & Months
    \end{tabular}
\end{center}

6b. What is your main purpose for being in Texas?

If reasons other than those listed, give an explanation in Part H.
\begin{list}{}{\leftmargin=0pt \itemindent=0pt \setlength{\itemsep}{0pt}}
    \item $\square$ Go to College
    \item $\square$ Establish/Maintain a Home
    \item $\square$ Work Assignment
\end{list}

7a. If you are a member of U.S. military, is Texas your Home of Record? {\color{red} If Yes, attach copy of DD-214.} (Yes/No/NA).
\vspace{0.6cm}
\underline{\hspace{3cm}}
\\
7b. What state will have been listed as your military legal residence for State tax purposes on your Leave and Earnings Statement for the 12 months prior to enrollment? (State).
\vspace{0.6cm}
\underline{\hspace{3cm}}
\\
8a. Do you hold the title (Warranty Deed, Deed of Trust, or other similar instrument that is effective to hold title) to residential real property in Texas for a period of at least a consecutive 12 months? {\color{red}If Yes, attach copy of Hold Title.} 
\begin{center}
    \begin{tabular}{c@{\hspace{2cm}}c@{\hspace{2cm}}c}
        \rule{4cm}{0.4pt} & \rule{4cm}{0.4pt} \\
        Yes/No & If yes, date required
    \end{tabular}
\end{center}

8b. Do you have ownership interest and customarily manage a business in Texas without the intention of liquidation in the foreseeable future for a period of at least a consecutive 12 months? \begin{center}
    \begin{tabular}{c@{\hspace{2cm}}c@{\hspace{2cm}}c}
        \rule{4cm}{0.4pt} & \rule{4cm}{0.4pt} \\
        Yes/No & If yes, date required
    \end{tabular}
\end{center}
9a. While living in Texas, have you been gainfully employed for a period of at least a consecutive 12 months?

Gainful employment requires an average employment of at least 20 hours per week for one year or earnings equal to at least half of tuition and living expense for one 9-month academic year. Employment conditioned on student status such as work-study, the receipt of stipends, fellowships, or research or teaching assistantships does not constitute gainful employment.

{\color{red}Students may be required to submit documentation of gainful employment in Texas.}
\\
(Yes/No).
\vspace{0.6cm}
\underline{\hspace{3cm}}
\\
9b. While living in Texas, have you received primary support through services from a social service agency for a period of at least a consecutive 12 months? (Yes/No).
\vspace{0.6cm}
\underline{\hspace{3cm}}
\\
10a. Are you married to a person who has been classified as a Texas resident by a Texas public institution or could answer "yes" to any part of question 8 or 9? (Yes/No).
\vspace{0.6cm}
\underline{\hspace{3cm}}
\\
10b. If yes, indicate which question (and which part of the question) could be answered "yes" by your spouse. 
\begin{list}{}{\leftmargin=0pt \itemindent=0pt \setlength{\itemsep}{0pt}}
    \item $\square$ 8a. Hold Title
    \item $\square$ 8b. Ownership Interest
    \item $\square$ 9a. Gainful Employment
    \item $\square$ 9b. Social Services Support
    \item $\square$ 10a. Texas Resident
\end{list}

10c. How long have you been married to the Texas resident? 
\begin{center}
    \begin{tabular}{c@{\hspace{2cm}}c@{\hspace{2cm}}c}
        \rule{4cm}{0.4pt} & \rule{4cm}{0.4pt} \\
        Years & Months
    \end{tabular}
\end{center}

\textbf{Part H. General Comments} \\[5pt]
Is there any additional information that you believe your college should know in evaluating your eligibility to be classified as a resident? If so, please provide it below: 
\\ \\
\begin{minipage}{1.0\textwidth}
\begin{framed}
Comments:
\vspace{2cm}
\end{framed}
\end{minipage}
\\ \\
\textbf{File Attachments} \\[5pt]
A minimum of two of the following supporting documents are required to complete your residency questionnaire:  
\noindent A minimum of two of the following supporting documents are required to complete your residency questionnaire:

\begin{itemize}
    \item Apartment lease, mortgage voucher, student/parent's name must be on the current lease and one that is 12 months old.
    \item Texas driver's license, showing a Texas address, student/parent's name must be on the current license and issued at least 12 months prior to the Census Date.
    \item Texas motor vehicle registration, student/parent's name must be on the current registration and issued at least 12 months prior to the Census Date.
    \item A current Texas voter registration card, student/parent's name must be on the current registration and issued at least 12 months prior to the Census Date.
    \item Two utility bills, student/parent's name must be on the current utility bills (one that is 12 months old) showing name and Texas address.
    \item Credit Report, showing the address length of time.
    \item TX High School Transcript (only for non-resident students)
\end{itemize}

\end{document}
